---
title: "mxnet"
author: "Vinh Dang"
date: "3/23/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

This is my implementation of using [mxnet](http://mxnet.io/) for the problem of digit recognition.

[Installation guide of mxnet for R](https://github.com/dmlc/mxnet/tree/master/R-package) is available.

# Load data

```{r}
require(mxnet)
train <- read.csv("../data/train.csv", header=TRUE)
test <- read.csv("../data/test.csv", header=TRUE)
train <- data.matrix(train)
test <- data.matrix(test)

train.x <- train[,-1]
train.y <- train[,1]
```

We can normalize the input data (originally values range from ``0`` to ``255`` as grayscale to between ``0`` and ``1``).

```{r}
train.x <- t(train.x/255)
test <- t(test/255)
```

# Build a neural network

## Deep Neural Network

Let's try with a feed-forward neural network.

```{r}
data <- mx.symbol.Variable("data")
fc1 <- mx.symbol.FullyConnected(data, name="fc1", num_hidden=128)
act1 <- mx.symbol.Activation(fc1, name="relu1", act_type="relu")
fc2 <- mx.symbol.FullyConnected(act1, name="fc2", num_hidden=64)
act2 <- mx.symbol.Activation(fc2, name="relu2", act_type="relu")
fc3 <- mx.symbol.FullyConnected(act2, name="fc3", num_hidden=10)
softmax <- mx.symbol.SoftmaxOutput(fc3, name="sm")
```

## Training

```{r}
devices <- mx.cpu()
mx.set.seed(0)
model <- mx.model.FeedForward.create(softmax, X=train.x, y=train.y,
                                     ctx=devices, num.round=10, array.batch.size=100,
                                     learning.rate=0.07, momentum=0.9,  eval.metric=mx.metric.accuracy,
                                     initializer=mx.init.uniform(0.07),
                                     batch.end.callback=mx.callback.log.train.metric(100))
```

## Prediction

```{r}
preds <- predict(model, test)
dim(preds)

pred.label <- max.col(t(preds)) - 1
table(pred.label)

submission <- data.frame(ImageId=1:ncol(test), Label=pred.label)
write.csv(submission, file='submission_dnn.csv', row.names=FALSE, quote=FALSE)
```

It should not take more than 1 minute on my Macbook Pro Mid-2014, and the accuracy is 97%.
